### 2022-05-11 manuscript.Rmd

@@

# Helper functions to re-format age from days to months + days
format_days_months <- function(days, long = FALSE) {
  m_str <- ifelse(long, " months ", "m ")
  d_str <- ifelse(long, " days", "d")
  days_per_month <- 30.417
  months <- days %/% days_per_month
  days_left <- as.integer(days - months * days_per_month)
  str <- paste0(as.character(months), m_str, as.character(days_left), d_str)
  str[is.na(days)] <- NA
  return(str)
}

# Helper function for printing percentages
print_perc <- function(x) scales::percent(x, accuracy = 0.1)

# Extract some descriptive statistics for usage in the main text
descs <- list(
  n_articles = length(unique(dat$article)),
  n_experiments = nrow(dat),
  n_infants = sum(dat$sample_size),
  percent_female = mean(dat$female_percent, na.rm = TRUE),
  min_age_months = as.integer(min(dat$age_min, na.rm = TRUE) / 30.417),
  max_age_months = as.integer(max(dat$age_max, na.rm = TRUE) / 30.417),
  mean_age_weighted = format_days_months(
    sum(dat$age_mean * dat$ni) / (sum(dat$ni)),
    long = TRUE
  ),
  n_experiments_habituation = nrow(filter(dat, task == "Habituation")),
  n_experiments_voe = nrow(filter(dat, task == "VoE"))
)
```

@@

```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
# Helper functions for printing numbers with exactly 2 decimal points
print_num <- function(x, digits = 2) {
  x <- format(round(x, digits), trim = TRUE, nsmall = digits)
  x[x == "NA"] <- NA
  return(x)
}

# Helper function for confidence intervals (optionally adding the mean)
print_ci <- function(lb, ub, mean = NULL) {
  mean_str <- ifelse(mean, paste0(print_num(mean), " "))
  paste0(mean_str, "[", print_num(lb), ", ", print_num(ub), "]")
}

# Get posterior draws for the effect in each experiment
epred_draws_brm <- epred_draws(res_brm, dat, ndraws = NULL) %>%
  mutate(experiment_f = factor(experiment))

# Create forest plot
dat %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_ci(ci_lb, ci_ub, mean = gi)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian highest posterior density intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_brm,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_brm,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_brm$intercept),
      print_num(summ_brm$intercept.lower),
      print_num(summ_brm$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add headers for each of the for columns
  annotate(
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = descs$n_experiments + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = descs$n_experiments + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "Lower",
      "Upper"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, descs$n_experiments + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

>>>>

# Load custom helper functions
source(here("manuscript_files", "helper_functions.R"))

@@

# Extract some descriptive statistics for usage in the main text
descs <- list(
  n_articles = length(unique(dat$article)),
  n_experiments = nrow(dat),
  n_infants = sum(dat$sample_size),
  percent_female = mean(dat$female_percent, na.rm = TRUE),
  min_age_months = as.integer(min(dat$age_min, na.rm = TRUE) / 30.417),
  max_age_months = as.integer(max(dat$age_max, na.rm = TRUE) / 30.417),
  mean_age_weighted = print_days_months(
    sum(dat$age_mean * dat$ni) / (sum(dat$ni)),
    long = TRUE
  ),
  n_experiments_habituation = nrow(filter(dat, task == "Habituation")),
  n_experiments_voe = nrow(filter(dat, task == "VoE"))
)
```

@@

```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
# Get posterior draws for the effect in each experiment
epred_draws_brm <- epred_draws(res_brm, dat, ndraws = NULL) %>%
  mutate(experiment_f = factor(experiment))

# Create forest plot
dat %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian highest posterior density intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_brm,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_brm,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_brm$intercept),
      print_num(summ_brm$intercept.lower),
      print_num(summ_brm$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add headers for each of the for columns
  annotate(
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = descs$n_experiments + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = descs$n_experiments + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "Lower",
      "Upper"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, descs$n_experiments + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )
